Geometric variational problems

### 2020-11-16 NSF2020/Description/preliminarywork.tex
yny Nov 15
yny Nov15b

\begin{wraptable}[8]{r}{0.55\textwidth}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
  moduli from the experimental literature and values derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
\begin{wraptable}[11]{l}{0.42\textwidth}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-5pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque respectively as a function of number of grid
  points $n$ per particle.  The data is for $N = 5$ particles; two of
  the particles are nearly touching at a distance 1\% of particle
  diameter.} 
\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters:  decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter 2.0 nm (the physical monolayer thickness, 2.0 nm~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.

@@

PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
date, we have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary. The specialized reciprocal
identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
torque (Table~\ref{tab:spectral_force}).
\begin{wrapfigure}[]{r}{0.5\textwidth}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s,
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
    mean angular velocities for the outer leaflet and the inner
    respectively.  Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}

>>>>

\vspace{-0.1cm}
\begin{wraptable}[8]{r}{0.53\textwidth}
\vspace{-0.1cm}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
  moduli from the experimental literature and values derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
%\begin{wraptable}[11]{l}{0.43\textwidth}
%\centering{
%  \begin{tabular}{|l|l|l|l|}
%    $n$   & (rel.~err.)$_F$
%    &  (rel.~err.)$_G$ \\
%    \hline
%% 32   &   4.07466     &   1.56437\\
%% 64   &   0.24664     &   0.03476\\
%% 128  &   0.00063     &   0.00006\\
%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
%  \end{tabular}}
%\vspace{-5pt}
%\caption{\label{tab:spectral_force} 
%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
%  and (rel.~err.)$_G = \max_{i}
%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
%  for force and torque respectively as a function of number of grid
%  points $n$ per particle.  The data is for $N = 5$ particles; two of
%  the particles are nearly touching at a distance 1\% of particle
%  diameter.} 
%\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters:  decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter 2.0 nm (the physical monolayer thickness, 2.0 nm~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.

@@

\begin{wraptable}[11]{l}{0.43\textwidth}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-5pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque respectively as a function of number of grid
  points $n$ per particle.  The data is for $N = 5$ particles; two of
  the particles are nearly touching at a distance 1\% of particle
  diameter.} 
\end{wraptable}
PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
date, we have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary. The specialized reciprocal
identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
torque (Table~\ref{tab:spectral_force}).

\begin{wrapfigure}[]{r}{0.5\textwidth}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s,
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
    mean angular velocities for the outer leaflet and the inner
    respectively.  Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
